Reasoning About a Machine with Local Capabilities

### 2018-05-06 toplas/paper.tex
Added ref to malloc spec.

  Our semantic model is not specific to a particular implementation of malloc,
  so rather than providing the implementation, we provide a specification that
  malloc must satisfy. The specification is a bit technical, but really just
  expresses standard expectations of how malloc should behave and this section
  can safely be skipped on first read.
  The malloc specification is presented in \figurename~\ref{fig:malloc-spec},
  and in the following, we will connect the description of the specification by
  referring to the item described.

>>>>

  Our semantic model is not specific to a particular implementation of malloc,
  so rather than providing the implementation, we provide a specification that
  malloc must satisfy. The specification is a bit technical, but really just
  expresses standard expectations of how malloc should behave and this section
  can safely be skipped on first read. The malloc specification is presented in
  \figurename~\ref{fig:malloc-spec} as Definition~\ref{spec:malloc}, and in
  the following, we will connect the description of the specification by
  referring to the item described.
